---
title: "Report Summary"
author: "Back Group"
output: html_document
---
```{r, echo=FALSE, include=FALSE}
library(knitr)
setwd(dir = "scripts")
source("summary_info.R")
source("table_summary.R")
champions<- read.csv("data/championsdata.csv", stringsAsFactors = FALSE)
runnerups <- read.csv("data/runnerupsdata.csv", stringsAsFactors = FALSE)
```
## Introductory Paragraph
  The National Basketball Assoication (NBA) has been around for almost 75 year and over the years the game of basketball has changed in my ways. The names of teams have changed, the unfiforms have changed, and even the way the game is played. For our project, we wanted to focus on the gameplay patterns and stats that have stayed consistent and that have changed. The data sets that we will be using are: a shot log from the 2014-2015 season and statistics on the individual games for both teams playing in the NBA finals from 1980 to 2018 (two seperate datasets).
<br> <br> The data for this research comes from:
<br> Champions Data: https://www.kaggle.com/daverosenman/nba-finals-team-stats
<br> Shot Logs data: https://www.kaggle.com/dansbecker/nba-shot-logs

```{r, echo=FALSE, include=FALSE}  
stats_1980s <- tpa_tp_pts(champions, runnerups, 1980, 1989)
stats_2018 <- tpa_tp_pts(champions, runnerups, 2018, 2018)
stats_2010s <- tpa_tp_pts(champions, runnerups, 2010, 2018)
```

The NBA was founded in 1946 but the 3-point field goal wasn't add until 1979. At the 1980 NBA championship game, there were only `r stats_1980s$tpa` attempted 3 point field goals and out of that `r stats_1980s$tpa` only 
`r stats_1980s$tp` were actually scored However, comparing those statistics to the 2018 NBA championship game, there is a dramatic difference. At 2018 championship, there were `r stats_2018$tpa` attempted 3 point field goals and `r stats_2018$tp` were made. Surprisingly, even though players have clearingly become more skilled at 3 point shoots, it hasn't made much of a difference in terms of the total points. From 1980 to 1989, the average points a team scored in a round of a championship game was `r stats_1980s$pts`. Today, from 2010 to 2018, the averge points a team scores in a round is `r stats_2010s$pts`. 

The two tables below, the total TPA (3 point fields attempts), the total TP (3 point fields made), and the total TPP (3 point percentage) stats for both teams who played at the NBA Championship game for a given year. The NBA championship has multiple rounds and the tabels below group all the rounds by year to find the team's total TPA and TP that year. Then the TPP is found by dividing the total TPA by total TP. This grouping of the rounds by years allows us to easily see how the team preformed that year in term onf 3-point related statstics. We choose to dislay the data in 5 year increments so it would easy to see these changes over time. Just looking at the 90s in comparison to the 80s, players cearly started taking more 3-point shoots and had drastic improvments from the 1980s NBA final. The TPP stays relatively the same because the ratio of TP to TPA is consistant, but the overall TP and TPA espically when comparing the 1980s & 1990s to the 2000s+.

## NBA Champion Winners 3-Pointer Statstics
```{r, echo = FALSE}
kable(table_function(champions, 1980, 1985, 1990, 1995, 2000, 2005, 2010, 2015, 2018), col.names = c("Year", "TPA", "TP", "TPP"))
```

## NBA Champion Runnerups 3-Pointer Statstics
```{r, echo = FALSE}
kable(table_function(runnerups, 1980, 1985, 1990, 1995, 2000, 2005, 2010, 2015, 2018), col.names = c("Year", "TPA", "TP", "TPP"))
```
