---
title: "Report Summary"
author: "Back Group"
output: html_document
---
```{r, echo=FALSE, include=FALSE}
library(knitr)
setwd(dir = "scripts")
source("summary_info.R")
source("table_summary.R")
champions<- read.csv("data/championsdata.csv", stringsAsFactors = FALSE)
runnerups <- read.csv("data/runnerupsdata.csv", stringsAsFactors = FALSE)
```
## Introductory Paragraph
  The National Basketball Assoication (NBA) has been around for almost 75 year and over the years the game of basketball has changed in my ways. The names of teams have changed, the unfiforms have changed, and even the way the game is played. For our project, we wanted to focus on the gameplay patterns and stats that have stayed consistent and that have changed. The data sets that we will be using are: a shot log from the 2014-2015 season and statistics on the individual games for both teams playing in the NBA finals from 1980 to 2018 (two seperate datasets).
<br> <br> The data for this research comes from:
<br> Champions Data: https://www.kaggle.com/daverosenman/nba-finals-team-stats
<br> Shot Logs data: https://www.kaggle.com/dansbecker/nba-shot-logs

```{r, echo=FALSE, include=FALSE}  
stats_1980s <- tpa_tp_pts(champions, runnerups, 1980, 1989)
stats_2018 <- tpa_tp_pts(champions, runnerups, 2018, 2018)
stats_2010s <- tpa_tp_pts(champions, runnerups, 2010, 2018)
```

The NBA was founded in 1946 but the 3-point field goal wasn't add until 1979. At the 1980 NBA championship game, there were only `r stats_1980s$tpa` attempted 3 point field goals and out of that `r stats_1980s$tpa` only `r stats_1980s$tp` were actually scored However, comparing those statistics to the 2018 NBA championship game, there is a dramatic difference. At 2018 championship, there were `r stats_2018$tpa` attempted 3 point field goals and `r stats_2018$tp` were made. Surprisingly, even though players have clearingly become more skilled at 3 point shoots, it hasn't made much of a difference in terms of the total points. From 1980 to 1989, the average points a team scored in a round of a championship game was `r stats_1980s$pts`. Today, from 2010 to 2018, the averge points a team scores in a round is `r stats_2010s$pts`. 

